\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-02-06 manuscript.Rmd
Knitting Version

Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA. We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). IRT assess the item quality by estimatingitem difficulty, item discrimination, a item information, and Test information [@bakerBasicsItemResponse2017]. Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. We discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. We also assessed the precision of the short LEBA using Test information curve (TIC). TIC  indicates the amount of information an the full-scale carry along the latent trait continuum. Item fit and person-fit of the fitted model were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018]. Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was consided adequate item fit. Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh < -2 was be considered as a misfit [@drasgow1985appropriateness].

```{r, MI. include =F}
# Among these nested models  configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal. Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently. Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups. This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.  We assessed the invariance model fit  using the fit by following the aforementioned guidelines of modelfit. The comparison among the MI models was made using 
```

@@

>>>>

Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA. We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). IRT assess the item quality by estimatingitem difficulty, item discrimination, a item information, and Test information [@bakerBasicsItemResponse2017]. Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. We discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. We also assessed the precision of the short LEBA using Test information curve (TIC). TIC  indicates the amount of information an the full-scale carry along the latent trait continuum. Item fit and person-fit of the fitted model were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018]. Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit. Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh < -2 was be considered as a misfit [@drasgow1985appropriateness].

```{r, MIdescription, include =F}
# Among these nested models  configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal. Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently. Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups. This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.  We assessed the invariance model fit  using the fit by following the aforementioned guidelines of modelfit. The comparison among the MI models was made using 
```

@@

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('appendix-1.Rmd')
```
